---
title: "Introduction to R"
author: "by Irimia Mihaela"
date: "2024-01-23"
output: html_document
---

```{=html}
<script type="text/javascript" async
  src="https://cdn.jsdelivr.net/npm/mathjax@3/es5/tex-mml-chtml.js">
</script>
```
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### [**Test - Introduction to R **]{style="color:blue"}
#### [**Analyzed data set:**]{style="color:blue"} [**pirates**]{style="color:red"}

Loading the necessary packages:
```{r , echo = FALSE, warning=FALSE, error=FALSE, message=FALSE}
# install.packages('yarrr')
library(yarrr)

library(tidymodels)
library(Hmisc)
library(tidyr)
library(lubridate)
library(psych)
library(readxl)
library(broom)
library(lm.beta)
library(yarrr)
# install.packages("lm.beta")
library(lm.beta)
require(devtools)
library(tidyverse)
library(lubridate)
library(DataEditR)
library(readxl)
library(RPostgres)
# install.packages("foreign")
library(foreign)
library(haven)
# install.packages('writexl')
library(writexl)
# install.packages('rio')
library(rio)
# install.packages('openxlsx')
library(openxlsx)
# install.packages('skimr')
library(skimr)
# install.packages('PerformanceAnalytics')
library(PerformanceAnalytics)
# install.packages('broom')
library(broom)
library(DataEditR)
library(psych)
# install.packages("pastecs")
library(pastecs) 
library(readr)
library(tidyverse)
library(janitor)
# install.packages('janitor')
options(scipen=999)
# install.packages('broom')
library (broom)
# install.packages('corrr')
library(corrr)
#install.packages("ggrepel")
# install.packages('ggrepel')
library(ggrepel)
# install.packages('corrplot')
library(corrplot)
# install.packages('car')
library(car)
# install.packages('corrgram')
library(corrgram)
# install.packages('DataExplorer')
library(DataExplorer)
library(carrier)
library(CARRoT)
```
#### Obiectivul analizei

::: {style="text-align: justify;"}
# [***Select pirates that have at least 5 tattoos or at least 5 parrots, have ‘Jack Sparrow’ as their favorite pirate, wear a headband, have a beard length of at least 15, and what are their records ordered by ID?***]{style="color:darkred;"}
:::

```{r, echo = TRUE, warning=FALSE, error=FALSE, message=FALSE}
selectie_pirates <- pirates %>%
  filter(tattoos >= 5 | parrots >= 5) %>%
  filter(favorite.pirate == "Jack Sparrow") %>%
  filter(headband == "yes") %>%
  filter(beard.length >= 15) %>%
  arrange(id)
selectie_pirates %>%
  head(10)
```
# [***Plot the heights and the weight of the pirates***]{style="color:darkred;"}
```{r, echo = TRUE, warning=FALSE, error=FALSE, message=FALSE}
class(pirates)
str(pirates)
```
the variables age and weight are numeric, so we will use a scatter plot for representation

the name of the variables
```{r, echo = TRUE, warning=FALSE, error=FALSE, message=FALSE}
names(pirates)
```

```{r, echo = TRUE, warning=FALSE, error=FALSE, message=FALSE}
plot(height ~ weight,  pirates) # the scatter plot
abline(coef(lm(height ~ weight, pirates)), col = 'blue', lwd = 3) # the regression line
```
```{r, echo = TRUE, warning=FALSE, error=FALSE, message=FALSE}

```

as we can see the relationship between weight and heights variables is linear  
```{r, echo = TRUE, warning=FALSE, error=FALSE, message=FALSE}

```
# [***Test if there is a difference between pirates with eye patch and those without eye patch***]{style="color:darkred;"}
```{r}

```

first we will test if the variance of the pirates with eye patch and that of the pirates without eye patch is equal or not
```{r}

```

checking the type of eye patch variable
```{r, echo = TRUE, warning=FALSE, error=FALSE, message=FALSE}
levels(pirates$eyepatch)
pirates$eyepatch <- as.factor(pirates$eyepatch)
```
setting the first group: pirates without eye patch
```{r, echo = TRUE, warning=FALSE, error=FALSE, message=FALSE}
levels(pirates$eyepatch) <- c('fara_petec', 'cu_petec')
```
testing the variance with Bartlett test  
```{r, echo = TRUE, warning=FALSE, error=FALSE, message=FALSE}
bartlett.test(beard.length~eyepatch, pirates, eyepatch %in%  c('fara_petec', 'cu_petec'))
```
or
```{r, echo = TRUE, warning=FALSE, error=FALSE, message=FALSE}
bartlett.test(beard.length~eyepatch, pirates)
```
Hypothesis:
```{r}

```

$$
H_0: \text{The variances of the groups are equal}
$$
```{r}

```

$$
H_1: \text{The variance of the groups is significantly different}
$$
```{r}

```

Decision:
$$
p\text{-value} < 0.05 \Rightarrow \text{we reject } H_0 \text{ with a 5\% risk of Type I error}
$$
$$
p\text{-value} \ge 0.05 \Rightarrow \text{fail to reject } H_0 \text{ at the 5\% significance level}
$$
Results
$$
p\text{-value} = 0.5579 > 0.05 \Rightarrow \text{fail to reject } H_0
$$

The variance between the groups is not statistically significant.
```{r}

```

Second 
we will test if there is a difference between pirates with eye patch and those without eye patch
we use the t test for independent samples
```{r, echo = TRUE, warning=FALSE, error=FALSE, message=FALSE}
t.test(beard.length~eyepatch, data = pirates, alternative = 'greater', var.equal=T)
```

Hypothesis
```{r}

```
$$
H_0: \text{There is no difference between the mean beard length (≥ 15) of pirates with an eye patch and those without an eye patch}
$$
```{r}

```
$$H_1:\mu_1 < \mu_2 {\text{ the differences are significant }} $$

Used test: t test
```{r}

```
Results:
```{r}

```
$$ {\text{ p-value = 0.07326 > 0,05 =>  accepting H_0. There is no significant differences between the analyzed groups   }}
$$
```{r}

```

# [***Checking the code for errors***]{style="color:darkred;"}
Can we compare the models?
```{r, echo = TRUE, warning=FALSE, error=FALSE, message=FALSE}
ms1<-lm(pirates$beard.length~pirates$height)
ms2<-lm(pirates$beard.length~pirates$weight+I(pirates$weight^2))
```
The models can not be compare, because the independent variables are not the same 
```{r, echo = TRUE, warning=FALSE, error=FALSE, message=FALSE}
anova(ms1, ms2)
```
```{r}

```
the value of the p-value is missing
```{r, echo = TRUE, warning=FALSE, error=FALSE, message=FALSE}
ms1<-lm(pirates$beard.length~pirates$height)
ms2<-lm(pirates$beard.length~pirates$height+I(pirates$height^2))
```
to be able to compere the two models the weight variable must be replace with height variable
```{r}

```

```{r, echo = TRUE, warning=FALSE, error=FALSE, message=FALSE}
anova(ms1, ms2)
```
```{r}

```
$$
H_0: \text{There is no difference between the models}
$$
```{r}

```
$$
H_1: \text{The complex model is better than the simple regression model }
$$
$$
p\text{-value} = 0.1438 > 0.05 \Rightarrow \text{fail to reject } H_0.
$$

There is no statistically significant difference between the models.


```{r}

```
# [***Transform a numerical variable into a variable with 3 classes***]{style="color:darkred;"} 

```{r}
str(pirates)
pirates$inaltime_cat<-cut(pirates$height, 3, c("Short", "Medium",  "Tall"))
```


# [***Estimate the regression model between tchests, age and pirates variables***]{style="color:darkred;"}
```{r}

```
To see if the tchests is correlated with age we will do a scatter plot
```{r}
plot(tchests ~ age,  pirates) 
abline(coef(lm(tchests ~ age, pirates)), col = 'blue', lwd = 3)
```
estimate the regression model
```{r}
reg_m <- lm(tchests ~ age, pirates)
```
the statistics of the estimated model

```{r}
summary(reg_m)
```
```{r}
formula(reg_m)
```

# Estimated equation
tchests = 0.2083 + 0.8217 * age

# Interpretation of the parameters

1. b0 = 0.2083  
The average number of chests discovered by a pirate is 0.2083 when age is equal to zero.

2. b1 = 0.8217  
When age increases by one year, the average number of discovered chests increases by 0.8217 chests.

# Testing the regression model (Multiple Linear Regression Model – MLRM)

H0: β1 = β2 = 0  
H1: At least one of the independent variable coefficients is different from zero

p-value = 0.0000000004082 < α = 0.05  
⇒ We reject the null hypothesis (H0) at the 5% significance level.

Interpretation:  
We can conclude that the regression model is statistically significant. Age has a statistically significant influence on the dependent variable (number of discovered chests).

# Model evaluation

Coefficient of determination:
R² = 0.03778  
→ 3.778% of the variation in the dependent variable (number of discovered chests) is explained by the variation in the independent variable (pirate’s age).  
The remaining variation is due to random factors not included in the model.

Adjusted R² = 0.03682  
→ 3.682% of the variation in the number of discovered chests is explained by age, after adjusting for the number of predictors in the model.

## Multiple Linear Regression Model

### Research objective

We want to examine whether the number of treasure chests discovered by a pirate varies depending on:
- the pirate’s age
- the number of grogg mugs consumed

The goal is to determine whether **age** and **grogg consumption** significantly influence the number of discovered chests.

---

## Estimated regression equation

$$
\widehat{tchests} = 5.4313 + 0.8328 \cdot age - 0.5449 \cdot grogg
$$

---

## Interpretation of the parameters

1. **Intercept ($\beta_0 = 5.4313$)**  

$$
\beta_0 = 5.4313
$$

The average number of discovered chests is 5.4313 when both age and the number of grogg mugs are equal to zero.

---

2. **Age coefficient ($\beta_1 = 0.8328$)**  

$$
\beta_1 = 0.8328
$$

When age increases by one year, the average number of discovered chests increases by 0.8328, holding grogg consumption constant.

---

3. **Grogg coefficient ($\beta_2 = -0.5449$)**  

$$
\beta_2 = -0.5449
$$

When the number of grogg mugs increases by one unit, the average number of discovered chests decreases by 0.5449, holding age constant.

---

## Testing the regression coefficients

For each parameter:

$$
H_0: \beta_i = 0
$$

$$
H_1: \beta_i \ne 0
$$

---

### Statistical decisions

- For $\beta_0$:  
  $$
  p\text{-value} = 0.2136 > 0.05 \Rightarrow \text{fail to reject } H_0
  $$  
  The intercept is not statistically significant.

- For $\beta_1$ (age):  
  $$
  p\text{-value} = 3.21 \times 10^{-10} < 0.05 \Rightarrow \text{reject } H_0
  $$  
  Age has a statistically significant effect on the number of discovered chests.

- For $\beta_2$ (grogg):  
  $$
  p\text{-value} = 0.0279 < 0.05 \Rightarrow \text{reject } H_0
  $$  
  Grogg consumption has a statistically significant effect on the number of discovered chests.

---

## Final interpretation

At the 5% significance level:

- There is a statistically significant linear relationship between **age** and the number of discovered chests.
- There is a statistically significant linear relationship between **grogg consumption** and the number of discovered chests.
- The intercept is not statistically significant.

## Confidence Intervals for the MLRM Parameters

### Confidence interval estimation (95%)

#### Intercept ($\beta_0$)

$$
CI_{95\%}(\beta_0) = [-2.6027,\; 46.0481]
$$

With 95% confidence, we can state that the true value of $\beta_0$ lies within this interval.  
Since the confidence interval contains 0, the intercept is **not statistically significant** at the 5% significance level.

---

#### Age coefficient ($\beta_1$)

$$
CI_{95\%}(\beta_1) = [0.4831,\; 1.0177]
$$

Because the confidence interval does not contain 0, there is a **statistically significant linear relationship** between the number of discovered chests and the pirate's age.

---

#### Grogg coefficient ($\beta_2$)

$$
CI_{95\%}(\beta_2) = [-1.0385,\; -0.0664]
$$

Since the confidence interval does not contain 0, there is a **statistically significant linear relationship** between the number of discovered chests and grogg consumption.

---

## Overall Significance of the Regression Model

### Hypotheses

$$
H_0: \beta_1 = \beta_2 = 0
$$

$$
H_1: \text{At least one independent variable coefficient is different from zero}
$$

Given:

$$
p\text{-value} = 4.082 \times 10^{-10} < 0.05
$$

We reject $H_0$ at the 5% significance level.

**Conclusion:**  
The regression model is statistically significant.

---

## Model Evaluation

### Coefficient of Determination

$$
R^2 = 0.04244
$$

4.244% of the variation in the number of discovered chests is explained jointly by age and grogg consumption.  
The remaining variation is due to other random factors not included in the model.

---

### Adjusted Coefficient of Determination

$$
R^2_{adj} = 0.04052
$$

After adjusting for the number of predictors, 4.052% of the variation in the dependent variable is explained by the independent variables.

---

# 7. Association Between Favorite Pirate and Sex

We test whether favorite pirate preferences differ by sex.

## Chi-Square Test of Independence

### Hypotheses

$$
H_0: \text{Favorite pirate and sex are independent}
$$

$$
H_1: \text{There is a significant association between favorite pirate and sex}
$$

Given:

$$
p\text{-value} = 1.181 \times 10^{-76} < 0.05
$$

We reject $H_0$ at the 5% significance level.

**Conclusion:**  
There is a statistically significant association between favorite pirate preference and the pirate’s sex.
